---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountGroupBy

<!-- badges: start -->
<!-- badges: end -->

The goal of CountGroupBy is to count the number of the value choose_value in the column group_by_column of the given dataset

## Installation

You can install the development version of countGroupBy from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-ziwei11")
```

## Example

This is a basic example which shows you how to count the number of data with '2017-02-02' in column issue_date and the number of data with 'New Building' in column type_of_work in the dataset datateachr::building_permits:

```{r example}
library(dplyr)
library(datateachr)
library(tidyr)
library(countGroupBy)

count_group_by(datateachr::building_permits, "issue_date", as.Date("2017-02-02", format = "%Y-%m-%d"))
count_group_by(datateachr::building_permits, "type_of_work", "New Building")

```

